Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-08-21 stp/paper_aaai/main.tex
Conclusion section

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.477688172043011)(2,0.543722761679028)(3,0.584279525763794)(4,0.560916442048518)(5,0.508442559100454)(6,0.451911027568922)(7,0.560410216718266)(8,0.627540834845735)(9,0.658907184769254)(10,0.494298245614035)(11,0.594547996272134)(12,0.572438909774436)(13,0.643132689678742)(14,0.544147521036133)(15,0.561388900346478)(16,0.620470013199142)(17,0.631330163644405)(18,0.644192377495463)(19,0.642924629016761)(20,0.656325397672681)(21,0.610482642157672)(22,0.628992740471869)(23,0.570074611816898)(24,0.679169187336157)(25,0.673558897243108)(26,0.667890182643746)(27,0.68742147145051)(28,0.709820528332325)
		    };
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.570063795853269)(2,0.756845238095238)(3,0.621034680606911)(4,0.719615829557505)(5,0.663677414539484)(6,0.680661881977671)(7,0.702849371292569)(8,0.730720679999118)(9,0.715323491375385)(10,0.722695511010729)(11,0.722586065299008)(12,0.725508681952266)(13,0.728214414334958)(14,0.753560036454773)(15,0.778231825645619)(16,0.745982043507288)(17,0.715855206037534)(18,0.733838894506235)(19,0.728435738081271)(20,0.754932383250967)(21,0.76774421230943)(22,0.761660230839754)(23,0.750358005521049)(24,0.82098385331144)(25,0.823507591442374)(26,0.834847535505431)(27,0.84013108540293)(28,0.813133718212162)
		    };
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.580144743457437)(2,0.699277168494516)(3,0.596982860940987)(4,0.683431847315197)(5,0.634133314342686)(6,0.630169810336433)(7,0.628025663269931)(8,0.642973856209151)(9,0.618457602339181)(10,0.616241290282443)(11,0.606940556177678)(12,0.605471976942706)(13,0.598988030767536)(14,0.608112237561116)(15,0.609841319882303)(16,0.578626150272492)(17,0.55776862026862)(18,0.57760989010989)(19,0.567994505494506)(20,0.492368742368742)(21,0.582722832722833)(22,0.574786324786325)(23,0.644688644688645)(24,0.658424908424909)(25,0.708791208791209)(26,0.716727716727717)(27,0.719373219373219)(28,0.708791208791209)
		    };
		%\legend{karma,serene,serene-pats}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.209547221954433)(2,0.411561264822134)(3,0.457295783926219)(4,0.449720026350461)(5,0.414575098814229)(6,0.364575098814229)(7,0.452173913043478)(8,0.526317523056654)(9,0.588158761528327)(10,0.403491436100132)(11,0.506175889328063)(12,0.489690382081687)(13,0.584008563899868)(14,0.470553359683795)(15,0.48570487483531)(16,0.553513584117033)(17,0.553774817136886)(18,0.573236677115987)(19,0.567816091954023)(20,0.580551201671891)(21,0.557301462904911)(22,0.559979101358412)(23,0.477098571926158)(24,0.57088122605364)(25,0.56078021595263)(26,0.565134099616858)(27,0.585336119818878)(28,0.598310693138279)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.558240946045824)(2,0.733876811594203)(3,0.610770750988142)(4,0.707559288537549)(5,0.654891304347826)(6,0.670421607378129)(7,0.704710144927536)(8,0.729611330698287)(9,0.716913702239789)(10,0.728837285902504)(11,0.724769433465085)(12,0.724670619235837)(13,0.727783267457181)(14,0.76187417654809)(15,0.790283267457181)(16,0.751266980146291)(17,0.72991118077325)(18,0.761259143155695)(19,0.742058516196448)(20,0.759103970741902)(21,0.776149425287357)(22,0.758842737722048)(23,0.730668756530825)(24,0.800330895158482)(25,0.800330895158482)(26,0.808951584813654)(27,0.813305468477882)(28,0.790229885057471)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.571875702946753)(2,0.770701581027668)(3,0.637285902503294)(4,0.73596837944664)(5,0.677618577075099)(6,0.693148880105402)(7,0.725263504611331)(8,0.750164690382082)(9,0.739640974967062)(10,0.743988801054019)(11,0.742094861660079)(12,0.734420289855072)(13,0.742934782608696)(14,0.775131752305666)(15,0.795965085638999)(16,0.772361546499478)(17,0.752899686520376)(18,0.776671891327064)(19,0.765308254963427)(20,0.733838383838384)(21,0.783986415882968)(22,0.774255485893417)(23,0.751219087425984)(24,0.803030303030303)(25,0.828456983629397)(26,0.83707767328457)(27,0.841431556948798)(28,0.828456983629397)
};
		 %\legend{karma,serene,serene-pats}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.28413987159729)(2,0.598592698574067)(3,0.36263108253479)(4,0.400362551212311)(5,0.387216985225677)(6,0.392432987689972)(7,0.394440889358521)(8,0.430805265903473)(9,0.438177883625031)(10,0.441894292831421)(11,0.461780428886414)(12,0.469180881977081)(13,0.477133095264435)(14,0.498149693012238)(15,0.512342214584351)(16,0.600962460041046)(17,0.5725257396698)(18,0.907191514968871)(19,0.551609396934509)(20,0.585879027843475)(21,0.610454380512239)(22,0.575962841510773)(23,0.657813549041748)(24,0.671637773513794)(25,0.689822912216188)(26,0.724388360977171)(27,0.750569899876912)(28,0.771229823430379)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.0166666666666667)(2,0.995)(3,0.8725)(4,0.8325)(5,0.9175)(6,0.965)(7,0.89)(8,0.9675)(9,0.96)(10,1.1225)(11,1.1475)(12,1.36)(13,1.295)(14,1.3925)(15,1.375)(16,1.4975)(17,1.9575)(18,2.11)(19,1.9075)(20,1.9175)(21,1.865)(22,1.915)(23,2.49)(24,2.4)(25,2.49)(26,2.49)(27,2.68333333333333)(28,2.47666666666667)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.025)(2,1.0375)(3,0.93)(4,1)(5,0.9575)(6,0.9425)(7,0.9)(8,0.975)(9,1.06)(10,1.2025)(11,1.2975)(12,1.9425)(13,1.52)(14,2.2825)(15,1.6275)(16,3.5375)(17,2.255)(18,2.1625)(19,6.505)(20,1.44666666666667)(21,2.2825)(22,2.3475)(23,8.28666666666667)(24,1.895)(25,8.3)(26,3.75333333333333)(27,3.73)(28,3.75)
};
		 %\legend{karma,serene,serene-pats}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (0,2.47666666666667)(1,7.15)(2,7.41)(3,8.83)(4,9.15)(5,9.32)(6,9.84)(7,10.04)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (0,3.75)(1,3.8)(2,3.84)(3,3.88666666666667)(4,3.93333333333333)(5,3.98)(6,4.03333333333333)(7,4.08)(8,4.13333333333333)(9,4.23)(10,4.29333333333333)(11,4.34)(12,4.38666666666667)(13,4.74)(14,4.83)(15,5.74333333333333)(16,5.96333333333333)(17,6.48666666666667)(18,6.53)(19,6.58333333333333)(20,6.63)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (0,3.74)(1,3.79)(2,3.83666666666667)(3,3.88666666666667)(4,3.93666666666667)(5,3.98666666666667)(6,4.03666666666667)(7,4.09333333333333)(8,4.17333333333333)(9,4.23)(10,4.31666666666667)(11,4.38)(12,4.54333333333333)(13,5)(14,6.17666666666667)(15,6.755)(16,1.61)(17,2.21)(18,2.35)(19,2.61)(20,3.11)
};
		\addplot[
		    color=brown,
		    mark=+,
		    ]
		    coordinates {
		    (0,3.75)(1,3.8)(2,3.84666666666667)(3,3.89666666666667)(4,3.95)(5,3.99666666666667)(6,4.05)(7,4.10333333333333)(8,4.16666666666667)(9,4.23333333333333)(10,4.43)(11,4.53333333333333)(12,4.78)(13,5.15333333333333)(14,5.36333333333333)(15,3.365)(16,1.91)(17,1.95)(18,8.42)(19,8.62)(20,8.85)
};
		 \addplot[
		    color=violet,
		    mark=star,
		    ]
		    coordinates {
		    (0,3.73666666666667)(1,3.78666666666667)(2,3.83666666666667)(3,3.88333333333333)(4,3.93666666666667)(5,3.98666666666667)(6,4.04333333333333)(7,4.09666666666667)(8,4.16)(9,4.22)(10,4.38333333333333)(11,4.49)(12,4.72333333333333)(13,4.99333333333333)(14,9.33333333333333)(15,10.715)(16,10.86)(17,10.915)(18,12.65)(19,20.35)(20,20.56)
};	
	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
		\end{axis}
\end{tikzpicture}
\subcaption{time (s)}\label{fig:soltime}
\end{minipage}%
\caption{Average precision, recall and time on the museum domain for leave-one-out strategy and different weighting scheme for patterns in serene.}\label{fig:perfsol}
\end{figure*}

%% sequential solution
As mentioned previously, the chuffed solver outputs solutions as it finds them.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions.
The idea is that the chuffed solver finds better solutions in terms of cost function, however, as we can see from the results,
that does not translate directly into more precise semantic models.
Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
i.e., costs of patterns are scaled by a factor.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we use a scaling factor 1 for pattern costs.
Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for patterns from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
This is a 20\% improvement in presision compared to the first solution found by \emph{serene-pats} and a 10\% improvement both in precision and recall for the first solution from \emph{serene}.
However, such improvement comes at a cost in run time.
On average, we have observed that the chuffed solver yields very good results already with the first found solution.
The sequential solutions are not always better, and hitting the optimal solution may take hours.

@@

\ddg{Isn't this really similar??}
\npr{It is very similar, I'm even using their code partially :)}

\section{Conclusion}
\ddg{TODO} 
In this paper we have introduced a new approach to solve the problem of relational-to-ontology schema mapping.

Future directions:
incorporate Linked Open Data and other external knowledge bases to overcome cold start problem;
incorporate schema and ontology constraints;
complex matches like 1:n and n:1 and iMap.

>>>>

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.517753313989873)(2,0.488688737671076)(3,0.51551313872799)(4,0.495118819099343)(5,0.527778910368045)(6,0.532176796157059)(7,0.566662366701066)(8,0.637110556563823)(9,0.685799234290614)(10,0.538089511412941)(11,0.621051710776405)(12,0.599367875333495)(13,0.670421793119162)(14,0.583598347357422)(15,0.623587223886899)(16,0.645277499838855)(17,0.653525664651826)(18,0.665572696108086)(19,0.670283086011174)(20,0.663804745401859)(21,0.633242908391853)(22,0.66099516031458)(23,0.644625119528521)(24,0.72069799334011)(25,0.737468671679198)(26,0.715572819263667)(27,0.727291592547725)(28,0.752558983666062)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.551714513556619)(2,0.682453503286837)(3,0.567702774084261)(4,0.646748619299324)(5,0.65492113250734)(6,0.701065228379203)(7,0.684439263401395)(8,0.700511175298951)(9,0.681034059961129)(10,0.685637253116215)(11,0.699316636125265)(12,0.697036509934383)(13,0.693463987436823)(14,0.704225209488367)(15,0.732978923190269)(16,0.724305489322319)(17,0.699459026247245)(18,0.716210056654951)(19,0.698987880687053)(20,0.733337516584389)(21,0.751908839952318)(22,0.75007040599401)(23,0.750592804644915)(24,0.814515445676703)(25,0.810987671748541)(26,0.817791638186375)(27,0.826003784931597)(28,0.809805364617137)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.598323207198336)(2,0.656420469232034)(3,0.551668227640311)(4,0.620327113896406)(5,0.623771074555817)(6,0.652894375155994)(7,0.625071981901494)(8,0.623287932111462)(9,0.601893257814311)(10,0.601192717220153)(11,0.602088073148115)(12,0.581718160067067)(13,0.570577347465439)(14,0.572274187082211)(15,0.581600752329829)(16,0.565774690293304)(17,0.5550594629542)(18,0.565097183518236)(19,0.524149694006153)(20,0.511449953555217)(21,0.576679655627024)(22,0.571388650336019)(23,0.546588180559473)(24,0.608169608169608)(25,0.608169608169608)(26,0.633066933066933)(27,0.634654234654234)(28,0.628305028305028)
};
		%\legend{karma,serene,serene-pats}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.300191975130116)(2,0.387168789342702)(3,0.418780803201093)(4,0.414852632606256)(5,0.449767567691694)(6,0.454560596014134)(7,0.472473240503931)(8,0.552403403170667)(9,0.618322253509807)(10,0.45708434156857)(11,0.540246526073466)(12,0.523083348403042)(13,0.603209776078489)(14,0.509054454749254)(15,0.54874878365927)(16,0.577977828772285)(17,0.583053944903167)(18,0.591126557438254)(19,0.592414794781259)(20,0.591100946357877)(21,0.575601120513223)(22,0.587190134384184)(23,0.575949431206362)(24,0.655469912102772)(25,0.649409306042166)(26,0.64025693035835)(27,0.652378142479562)(28,0.666045239412379)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.517923133776792)(2,0.667141218952813)(3,0.56262382276875)(4,0.646790367442541)(5,0.651735815098987)(6,0.706388551614468)(7,0.698383379116542)(8,0.714984169630376)(9,0.700346244485205)(10,0.704664218197892)(11,0.717929077647748)(12,0.711690361988742)(13,0.707592621296799)(14,0.725417933239758)(15,0.760334088253952)(16,0.741766948274724)(17,0.726258869970838)(18,0.748428390280994)(19,0.723282293295816)(20,0.746991608671798)(21,0.769430045325921)(22,0.751719414109543)(23,0.756837646239269)(24,0.816669125330383)(25,0.816669125330383)(26,0.821841539123487)(27,0.824453869322024)(28,0.810608519269777)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.592810513524547)(2,0.704036744254136)(3,0.580300590445518)(4,0.665729761381935)(5,0.671789291034815)(6,0.721540066765983)(7,0.718258458411911)(8,0.728686409419572)(9,0.71549775963672)(10,0.719667189083217)(11,0.729479363111076)(12,0.713288181617252)(13,0.723866470903981)(14,0.739158277862456)(15,0.764121967041831)(16,0.755829992510182)(17,0.746486501253236)(18,0.758703555728573)(19,0.723655728717502)(20,0.729409784115667)(21,0.774654705722995)(22,0.768167419063295)(23,0.754561938768098)(24,0.828459715477971)(25,0.828459715477971)(26,0.838717192206036)(27,0.841329522404573)(28,0.833544778412933)
};
		 %\legend{karma,serene,serene-pats}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (1,0.268540382385254)(2,0.485812822977702)(3,0.346803307533264)(4,0.372188647588094)(5,0.367514610290527)(6,0.37602166334788)(7,0.376668055852254)(8,0.410835981369019)(9,0.422285079956055)(10,0.424292365709941)(11,0.439166347185771)(12,0.446258664131165)(13,0.46294093132019)(14,0.484450976053874)(15,0.489395022392273)(16,0.550653139750163)(17,0.543892900149027)(18,0.760240634282429)(19,0.529818336168925)(20,0.544886191685995)(21,0.576984961827597)(22,0.557323813438416)(23,0.563650608062744)(24,0.60092453956604)(25,0.626034975051881)(26,0.663434648513793)(27,0.692028045654297)(28,0.702148389816284)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (1,0.0175)(2,0.665)(3,0.585)(4,0.561666666666667)(5,0.62)(6,0.655)(7,0.605)(8,0.66)(9,0.655)(10,0.766666666666667)(11,0.783333333333333)(12,0.933333333333333)(13,0.901666666666667)(14,0.968333333333333)(15,0.956666666666667)(16,1.03333333333333)(17,1.34166666666667)(18,1.44666666666667)(19,1.30833333333333)(20,1.31333333333333)(21,1.27833333333333)(22,1.31333333333333)(23,1.28166666666667)(24,1.472)(25,1.526)(26,1.528)(27,1.642)(28,1.52)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (1,0.02)(2,0.696666666666667)(3,0.619166666666666)(4,0.67)(5,0.65)(6,0.64)(7,0.615833333333333)(8,0.674166666666667)(9,0.741666666666667)(10,0.8375)(11,0.9125)(12,1.62)(13,1.05)(14,1.94583333333333)(15,1.11916666666667)(16,2.85916666666667)(17,1.55583333333333)(18,1.53666666666667)(19,3.27)(20,1.399)(21,1.63833333333333)(22,1.66)(23,3.24181818181818)(24,3.64444444444444)(25,3.69777777777778)(26,2.343)(27,2.334)(28,2.373)
};
		 %\legend{karma,serene,serene-pats}

@@

		\addplot[
		    color=blue,
		    mark=square,
		    ]
		    coordinates {
		    (0,2.47666666666667)(1,7.15)(2,7.41)(3,8.83)(4,9.15)(5,9.32)(6,9.84)(7,10.04)
};
		\addplot[
		    color=red,
		    mark=*,
		    ]
		    coordinates {
		    (0,3.75)(1,3.8)(2,3.84)(3,3.88666666666667)(4,3.93333333333333)(5,3.98)(6,4.03333333333333)(7,4.08)(8,4.13333333333333)(9,4.23)(10,4.29333333333333)(11,4.34)(12,4.38666666666667)(13,4.74)(14,4.83)(15,5.74333333333333)(16,5.96333333333333)(17,6.48666666666667)(18,6.53)(19,6.58333333333333)(20,6.63)
};
		\addplot[
		    color=green,
		    mark=x,
		    ]
		    coordinates {
		    (0,3.74)(1,3.79)(2,3.83666666666667)(3,3.88666666666667)(4,3.93666666666667)(5,3.98666666666667)(6,4.03666666666667)(7,4.09333333333333)(8,4.17333333333333)(9,4.23)(10,4.31666666666667)(11,4.38)(12,4.54333333333333)(13,5)(14,6.17666666666667)(15,6.755)(16,1.61)(17,2.21)(18,2.35)(19,2.61)(20,3.11)
};
		\addplot[
		    color=brown,
		    mark=+,
		    ]
		    coordinates {
		    (0,3.75)(1,3.8)(2,3.84666666666667)(3,3.89666666666667)(4,3.95)(5,3.99666666666667)(6,4.05)(7,4.10333333333333)(8,4.16666666666667)(9,4.23333333333333)(10,4.43)(11,4.53333333333333)(12,4.78)(13,5.15333333333333)(14,5.36333333333333)(15,3.365)(16,1.91)(17,1.95)(18,8.42)(19,8.62)(20,8.85)
};
		 \addplot[
		    color=violet,
		    mark=star,
		    ]
		    coordinates {
		    (0,3.73666666666667)(1,3.78666666666667)(2,3.83666666666667)(3,3.88333333333333)(4,3.93666666666667)(5,3.98666666666667)(6,4.04333333333333)(7,4.09666666666667)(8,4.16)(9,4.22)(10,4.38333333333333)(11,4.49)(12,4.72333333333333)(13,4.99333333333333)(14,9.33333333333333)(15,10.715)(16,10.86)(17,10.915)(18,12.65)(19,20.35)(20,20.56)
};	
	%\legend{serene,pats-1,pats-5,pats-10,pats-20}
		\end{axis}
\end{tikzpicture}com
\subcaption{time (s)}\label{fig:soltime}
\end{minipage}%
\caption{Average precision, recall and time on the museum domain for leave-one-out strategy and different weighting scheme for patterns in serene.}\label{fig:perfsol}
\end{figure*}

%% sequential solution
As mentioned previously, the chuffed solver outputs solutions as it finds them.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we report the first found solutions.
In Fig.~\ref{fig:perfsol} we show how the performance of \emph{serene} changes across sequentially found solutions for the museum domain.
The idea is that the chuffed solver finds better solutions in terms of cost function, however, as we can see from the results,
that does not translate directly into more precise semantic models.
Additionally, we investigate how the performance is influenced if we introduce a weighting scheme on the patterns,
i.e., costs of patterns are scaled by a factor.
In Fig.~\ref{fig:perfmuseum} and~\ref{fig:perfsoccer} we use a scaling factor 1 for pattern costs.
Fig.~\ref{fig:perfsol} demonstrates that by using scaling factors 5, 10 or 20 for pattern costs from the museum domain we can generate semantic models which are almost 90\% in precision and recall.
This is a 20\% improvement in presision compared to the first solution found by \emph{serene-pats} and a 10\% improvement both in precision and recall for the first solution from \emph{serene}.
Yet such improvement comes at a cost in run time.
On average, we have observed that \emph{serene} yields very good results already with the first solution found found by the chuffed solver.
\emph{Serene-pats}, on the other hand, produces considerably better solutions with scaled pattern costs and sequential solutions.
However, the sequential solutions are not always better, and hitting the optimal solution may take hours.

We have also observed that \emph{serene-pats} manages to find the ground truth on many instances among its sequential solutions, but again it takes much more time.
In the end, which approach to use for \relonto{} problem comes down to trade-offs between precision, recall and time.

@@

%\ddg{Isn't this really similar??}
%\npr{It is very similar, I'm even using their code partially :)}

\section{Conclusion}
\ddg{TODO} 
In this paper we have introduced a new approach \emph{serene} to solve the problem of relational-to-ontology schema mapping \relonto{}.
We have also built its extension \emph{serene-pats} which uses additionally frequent graph patterns.
Our experiments on two domains \emph{museum} and \emph{soccer} demonstrate that \emph{serene} generates on average more consistent semantic models in terms of precision and recall compared to the state-of-the-art system \emph{karma}.
The modified version \emph{serene-pats} produces, on average, better semantic models in terms of recall, however, its overall performance is rather mixed if we consider the first produced model.
However, the solutions discovered by \emph{serene-pats} afterwards tend to be much better both in precision and recall.
The disadvantage is though that it comes at a cost of run time.
In the end, which approach to use for \relonto{} problem comes down to trade-offs between precision, recall and time.

%%%%%%%%future directions%%%%%%%%%%%%%
% cold start problem and LOD
One of the key limitations of our approach is the availability of training data in the domain, which is often referred to as cold start problem.
We consider leveraging the data from the Linked Open Cloud (LOD) which, on one hand, leads to improved performance in the light of insufficient data and, on the other hand, helps in publishin consistent Linked Data~\cite{Taheriyan:Leveraging}. 
As we have shown, the frequent graph pattern mining procedure DIMSpan~\cite{petermann2017dimspan} which we use in our work is a highly scalable approach compared to the technique based on SPARQL queries from~\cite{Taheriyan:Leveraging}.

%incorporate schema and ontology constraints
Incorporating schema and ontology constraints may also help with the cold start problem.
Furthermore, it can provide means to improve disambiguation of properties.
For example, it is hard for our system to differentiate between startDate and endDate of the class Event.
Having a constraint that startDate is before endDate might improve the mapping in such situations.

%complex matches
Another interesting direction for further research is to recognise complex matches.
Our semantic labeling model \emph{serene} as well as many others in the literature~\cite{Pham:semantic}\cite{Ritze:matching} can learn only one-to-one matches between attributes and properties in the ontology.
\cite{Pinkel:rodi} show that such systems as BootOX can also handle efficiently only one-to-one matches while their performance degrades considerably for $1:n$ and $n:1$ matches.
\emph{Karma}~\cite{taheriyan2016learning} offers its users to manually specify tranformations through Python scripts.
\cite{Dhamankar:imap} offer a way to learn such transformations from the historic data.
This is one of the features which we want to incorporate into \emph{serene}.
